### 2016-03-18 section/5_exper.tex
linhai, pls fill XXX

\section{Evaluation}
\label{sec:experiment}

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccc}
    \toprule
   {\bf BugID}           &  {\bf KLOC}     &  {\bf P. L.}           & {\bf RootCause}  & {\bf Fix}\\
   \midrule
   Mozilla347306         & 88              & C                      &  0*1?        & C     \\
   Mozilla416628         & 105             & C                      &  0*1?        & C     \\
   Mozilla490742         &  -             & JS                     &  C-I         & B       \\
   Mozilla35294          &  -             & C++                    &  C-L         & B        \\ 
   Mozilla477564         &  -             & JS                     &  C-L         & M       \\
   \midrule 
   MySQL27287            & 995             & C++                    &  0*1?,C-L        & C     \\
   MySQL15811            & 1127            & C++                    &  C-L         & M \\ 
   \midrule    
   Apache32546           &  -             & Java                   &  C-I         & B  \\
   Apache37184           &  -             & Java                   &  C-I         & M  \\
   Apache29742           &  -             & Java                   &  C-L         & B \\ 
   Apache34464           &  -             & Java                   &  C-L         & M  \\
   Apache47223           &  -             & Java                   &  C-L         & B \\
   \midrule
   GCC46401              & 5521            & C                      &  [0$|$1]*    & S   \\
   GCC1687               & 2099            & C                      &  C-I         & M \\
   GCC27733              & 3217            & C                      &  C-I         & M \\
   GCC8805               & 2538            & C                      &  C-L         & B\\
   GCC21430              & 3844            & C                      &  C-L         & M \\
   GCC12322              & 2341            & C                      &  1*          & S\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Benchmark information.
  (-: benchmarks extracted from real-world applications.
  ``C-I'': cross-iteration redundancy.
  ``C-L'': cross-loop redundancy.
  C, B, M, S: fix strategies as discussed in
  Table \ref{tab:root}.
  ) 
 }
  \label{tab:benchmarks}
\end{table}

@@

\paragraph{Benchmarks}
We use 18 out of the 45 bugs listed in Table \ref{tab:root} as our 
evaluation benchmarks. Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
The remaining bugs listed in Table \ref{tab:root} are much more difficult to
use as benchmarks, 
either because they depend on special hardware/software environment
or because they involve too complex data structures to extract. 
Overall, these 18 bugs cover a wide variety of performance root causes, as 
shown in Table~\ref{tab:benchmarks}.

@@

\paragraph{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For 14 out of the 18 benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining
benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcc}
    \toprule
                            	&  {\bf Reported}             &{\bf Fix }                     \\
   {\bf BugID}                  &  {\bf Root Cause}           &{\bf Suggestion}             \\
   \midrule
   Mozilla347306                & \Yes                        & \Yes                                          \\
   Mozilla416628                & \Yes                        & \Yes                                         \\
   Mozilla490742                & \Yes                        & \Yes                                             \\
   Mozilla35294                 & \Yes                          & \Yes                                              \\ 
   Mozilla477564                & \Yes                          & \Yes                                            \\
   \midrule 
   MySQL27287                   & \Yes                          & \ding{55}                                         \\
   MySQL15811                   & \Yes                          & \Yes                                      \\ 
   \midrule    
   Apache32546                  & \Yes                          & \Yes                                      \\
   Apache37184                  & \Yes                          & \Yes                                        \\
   Apache29742                  & \Yes                          & \Yes                                       \\ 
   Apache34464                  & \Yes                          & \Yes                                        \\
   Apache47223                  & \Yes                          & \Yes                                       \\
   \midrule
   GCC46401                     & \Yes                     & \Yes                                      \\
   GCC1687                      & \Yes                          & \Yes                                     \\
   GCC27733                     & \Yes                          & \Yes                                     \\
   GCC8805                      & \Yes                          & \Yes                                  \\
   GCC21430                     & \Yes                          & \Yes                                     \\
   GCC12322                     & \Yes                         & \ding{55}                                   \\
\bottomrule
   \end{tabular}
  %\nocaptionrule
\vspace{-0.1in}
  \caption{Coverage Results.}
\vspace{-0.1in}
  \label{tab:cover}
\end{table}

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
\Tool identifies the correct root cause for \textbf{all} 18 benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 16 out of 18 cases. There are only two cases where \Tool fails to suggest
the fix strategy that developers used. For MySQL\#27287, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
find a new data structure that can eliminate both root causes.
For GCC\#12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. However, GCC developers feel
that it is worthwhile considering the slow-down caused by the original loop.

@@

\begin{table}
  \centering
  \small
  \newcommand{\Yes}[0]{\checkmark}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lcccccc}
    \toprule
   {\bf BugID}           &  {\bf 0*1?}          &  {\bf [0$|$1]*}             &{\bf C-I$_b$}            &{\bf C-I$_m$}          &   {\bf C-L}     & {\bf Total}  \\
   \midrule
   Mozilla347306         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla416628         &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla490742        &   -                  & -                           & -                       & -                     &   -             & -\\
   Mozilla35294         &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Mozilla477564         &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule 
   MySQL27287            &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   MySQL15811            &   -                  & -                           & -                       & -                     &   -             & -\\ 
   \midrule    
   Apache32546           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache37184           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache29742       &   -                  & -                           & -                       & -                     &   -             & -\\ 
   Apache34464           &   -                  & -                           & -                       & -                     &   -             & -\\
   Apache47223           &   -                  & -                           & -                       & -                     &   -             & -\\
   \midrule
   GCC46401              &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC1687               &   -                  & -                           & -                       & -                     &   -             & -\\
   GCC27733            &   -                  & -                           & -                       & -                     &   -             & - \\
   GCC8805               &   -                  & 0$_1$                       & -                       & -                     &   -             & 0$_1$\\
   GCC21430              &   0$_1$              & 0$_3$                       & -                       & 0$_1$                 &   0$_1$         & 0$_6$\\
   GCC12322              &   0$_1$              & 0$_1$                       & -                       & 0$_1$                 &   0$_1$         & 0$_4$\\
\bottomrule
   \end{tabular}
  %\nocaptionrule
\vspace{-0.1in}
  \caption{False positives of \Tool for top 5 loops reported by 
    statistical debugging for each benchmark. `-': no false positive. $x_y$: real ($x$) and benign false positives ($y$).
}
  \label{tab:top5}
\end{table}

As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
false positive and 14 benign false positives for all the top 5 loops.

@@

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 11 out of the
13 benign cases. In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
The remaining two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.

The accuracy of \Tool benefits from its run-time analysis.
For example, there are 7 benchmarks in total that each contains
a loop that generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the total number of iterations and
correctly identifies 3 of them as truly inefficient and severe enough
to cause the corresponding performance problem.

@@

\comment{
\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
                       & {\bf Resultless} &  \multicolumn{2}{c}{\bf C-L R. } & \multicolumn{2}{c}{\bf C-I R.}\\
      \cmidrule(lr){3-4}    
      \cmidrule(lr){5-6}   
     {\bf BugID}       &                & Not               &  S.+O.            & Not                & S.+O.  \\
     \midrule
     Mozilla347306     & 1.07\%         & 303.37{\bf X}     &  22.40\%       & 467.74{\bf X}         & 10.17\%      \\
     Mozilla416628     & 0.80\%         & 56.51{\bf X}      &  4.10\%        & 84.6{\bf X}           & 2.99\%\\
     \midrule
     MySQL27287        & $sim$0        & 108.55{\bf X}     &  1.66\%        & 351.07{\bf X}         & - \\
     MySQL15811        &  -             & 226.04{\bf X}     &  0.03\%        & 423.44{\bf X}         & - \\
     \midrule
      GCC46401         & 3.12\%         & 20.07{\bf X}      &  3.80\%        & 37.44{\bf X}          & 5.95\%\\ 
      GCC1687          & -              & /                 &  /             & 141.29{\bf X}         & $\sim$0 \\
      GCC27733         & $\sim$0        & /                 &  /             & 16.41{\bf X}          & 4.73\%         \\
      GCC8805          & -              & 1.22{\bf X}       & $\sim$0        & 2.52{\bf X}           & $\sim$0\\
      GCC21430         & -              & 106.20{\bf X}     & 5.46\%         & 158.89{\bf X}         & 0.69\%\\
      GCC12322         & -              & 20.07{\bf X}      & 1.75\%         & 37.44{\bf X}          & $\sim$0\\
  \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop. 
    Only performance results from non-extracted benchmarks are shown here. 
  Not: not applying the performance optimization in \Tool.
  -: static analysis can figure out the results and hence no dynamic analysis is conducted.
  /: not applicable. }
  \label{tab:performance}
\end{table}
}

@@

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
Mozilla\#347306 still incurs the largest overhead (0.49\%). 
The diagnosis results remain the same for all but
GCC\#12322, where too few samples are available
to judge redundancy.

When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
Mozilla\#347306 has the largest overhead (4.47\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
The diagnosis results remain 
the same for all but GCC\#12322.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless
loop checking.

@@

>>>>

\section{Evaluation of \Tool}
\label{sec:experiment}

@@

\input section/tab_benchmarks

@@

\paragraph{Benchmarks}
Note that \Tool is a tool that helps diagnose performance problems that
have already manifested, not a detection tool that can help predict not-yet-manifested
problems. Consequently, our benchmarks are performance problems that have already
happened in real world, and we will reproduce these problems to evaluate \Tool.
To conduct a thorough evaluation, we use
benchmarks from two sources.

First, we evaluate \Tool on 18 out of the 45 bugs listed in Table \ref{tab:root}. 
Among these 18, seven are extracted from Java or JavaScript
programs and re-implemented in C++, as \Tool currently only handles C/C++
programs; one is extracted from a very old version of Mozilla.
%These 18 bugs include all the benchmarks used in the recent
%statistical performance debugging work~\cite{SongOOPSLA2014}.
The extraction is conducted by XXX.
We did not use the remaining 27 bugs listed in Table \ref{tab:root}
as benchmarks, 
either because they depend on special hardware/software environment
or because they involve too complex data structures to extract XXX. 
Overall, these 18 bugs cover a wide variety of inefficiency root causes, as 
shown in Table~\ref{tab:benchmarks}.

Second, we evaluate \Tool on 21 out of the xx bugs in the benchmark
suite of Toddler \cite{Alabama}.
All of these bugs come from Java programs. We extract XXX (how did you
extract exactly?) and re-implement in C++. Each extracted benchmark 
contains 4--5 loops (how come you always have 4--5 loops??XXX). 
Note that, Toddler focuses on inefficient nested loops, and its
benchmark bugs only cover two types of inefficiency root causes,
as shown in Table \ref{tab:benchmarks}.
We use Toddler benchmark suite because it provides a larget set of
repeatable inefficient loop problems.

@@

\paragraph{Evaluation settings}
Our evaluation uses existing statistical performance diagnosis
tool \cite{SongOOPSLA2014} to process a performance problem and identify 
one or a few suspicious loops for \Tool to analyze.
For 14 out of the 18 benchmarks, statistical debugging identifies the
real root-cause loop as the most suspicious loop. For the remaining
benchmarks, the real root-cause loops are ranked number 2, 2, 4, and 10.
%Overall, we believe future tools can accurately identify the most one or a couple
%of suspicious loops.
XXX (what can we say about Toddler benchmark set here?)

\input section/tab_cover

@@

\subsection{Coverage Results}
\label{sec:coverage}
Overall, \Tool provides good diagnosis coverage, as shown in Table~\ref{tab:cover}. 
\Tool identifies the correct root cause for \textbf{all} \allbugs benchmarks, and 
suggests fix strategies that exactly match what developers took in practice
for 33 out of \allbugs cases.

The six cases where the fix strategy suggested by \Tool does not match that of 
developers fall into three categories.
First, the fix strategy taken by developers is a subset of what suggested by 
\Tool.
For MySQL\#27287 and Apache\#53622, the root-cause loop
is both cross-loop redundant and 0*1? inefficient. \Tool suggests both changing
data structures and memoization as fix strategies. In practice, the developers
only changed the data structure, which eliminated both types of inefficiency,
in case of MySQL\#27287, or the main type of inefficiency, in case of Apache\#53622.

Second, the fix strategy taken by developers is a superset of what suggested by
\Tool.
In Collections bugs \#407, \#408, and \#425, XXX.

Third, \Tool cannot suggest fix strategy for 1* loops.
For GCC\#12322, \Tool correctly tells that the loop under study
does not contain any form of inefficiency and produce results in every 
iteration, and hence fails to suggest any fix strategy. In practice, GCC
developers decide to skip the loop, which will cause some programs compiled by
GCC
to be less performance-optimal than before. However, GCC developers feel
that it is worthwhile considering the slow-down caused by the original loop.

@@

\input section/tab_top5

As shown in Table \ref{tab:top5}, \Tool is accurate, having 0 real
false positive and 23 benign false positives for all the top 5 loops
of the \allbugs benchmarks.

@@

There are several reasons for these benign performance problems. 
The main reason is that they are not the main contributor to the 
performance problem perceived by the users. This happens to 11 out of the
13 benign cases (XXX subject to change XXX). 
In fact, this is not really a problem for \Tool in 
real usage scenarios, because statistical debugging can accurately
tell that these loops are not top contributors to the performance
problems.
Two cases happen when fixing the 
identified redundant/resultless problems
are very difficult and hence developers decide not to fix them.
The remaining cases XXX.

The accuracy of \Tool benefits from its run-time analysis.
For example, there are 7 (XXX to change XXX) benchmarks in total that each contains
a loop that generates side effect only
in its last iteration. Without run-time information, \Tool would judge
all of them as inefficient (0*1? resultless). Fortunately,
\Tool run-time counts the total number of iterations and
correctly identifies 3 (XXX to change XXX) of them as truly inefficient and severe enough
to cause the corresponding performance problem.

@@

@@

When we lower the sampling rate from 1/100 to 1/1000 
in cross-loop redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#347306 still incurs the largest overhead (0.49\%). 
The diagnosis results remain the same for all but
GCC\#12322, where too few samples are available
to judge redundancy.

When we lower the sampling rate from 1/1000 to 1/10000
in cross-iteration redundancy analysis,
among all the benchmarks in Table \ref{tab:performance},
Mozilla\#347306 has the largest overhead (4.47\%). 
%In fact, Mozilla347306 is the only one whose overhead is larger than 2\%. 
The diagnosis results remain 
the same for all but GCC\#12322.
%If we increase the sampling rate to 1/100, we will 
%have two benchmarks whose overhead is larger than 30\%.

\paragraph{Resultful and redundancy rate}
Since the severity of resultless and redundant loops depends on
workload, it is natural that \Tool uses two thresholds in its diagnosis.
In fact, the diagnosis results are largely insensitive to the threshold
setting. For example, the results would remain the same when
changing the redundancy rate threshold from 0.5 to any value between about
0.1 and 0.66. We will have 1 more false negative and 1 fewer benign false positive, 
when the rate is 0.7. The trend is similar for resultless
loop checking. 
XXX

@@

\subsection{Comparison with other tools}
XXXXXX
